Title

### 2015-12-09 paper/paper.tex
update for changed example AMR
pagebreak after ToC, since it's getting long
add information ordering

\begin{document}
\maketitle
\tableofcontents

@@

Abstract Meaning Representation (AMR)\cite{amr_sembank} attempts to unify the
semantic representation of natural language sentences. Unlike syntactic
annotations, semantic annotations often differ for different semantic relations
(named entities, temporal entities, co-referencing, etc). AMR, by contrast,
provides a single, graphical representation of the logical meaning of a
sentence, which can be easily understood by both humans and computers. For
example, given the sentence ``Prosecutors in South Korea seized 80 kilograms of
drugs'', we can construct the following logical form and AMR.\\

@@

>>>>

\begin{document}
\maketitle
\tableofcontents
\pagebreak

@@

Abstract Meaning Representation (AMR)\cite{amr_sembank} attempts to unify the
semantic representation of natural language sentences. Unlike syntactic
annotations, semantic annotations often differ for different semantic relations
(named entities, temporal entities, co-referencing, etc). AMR, by contrast,
provides a single, graphical representation of the logical meaning of a
sentence, which can be easily understood by both humans and computers. For
example, given the sentence ``A prosecutor in South Korea seized 80 kilograms
of drugs'', we can construct the following logical form and AMR.\\

@@

Information ordering is an integral component of the Discourse Planning phase
of the NLG pipeline, discussed above and in \cite{applied_nlg}. After an
information set has been structured into to pieces of information (``facts" or
sentences), these pieces need to be ordered so that the reader can process and
understand the information being conveyed as easily as possible. This is often
approached as a planning problem, though Reiter and Dale explore using decision
trees and instance-based learning.
